Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-09 prop_letter.tex
prop_letter.tex \section{Born} Updating...

Recall in Sec.~\ref{sec:fuzzy}, we illustrate the non-constructive
postulates for the quantum probability measures first, and then introduce
the Born rule which induces a quantum probability measures from each
state. Since the postulates for QIVPMs in Sec.~\ref{sec:Interval-Uncertainty}
are also non-constructive, we also want to find a simple rule to construct
a QIVPM. Notice that the biggest difference between a quantum probability
measure~$\mu:\events\rightarrow\left[0,1\right]$ and a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
is their ranges. If there is a function~$\iota$ mapping a number~$x\in\left[0,1\right]$
to an interval~$\iota\left(x\right)\in\mathscr{I}$, then we can
concatenate it with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
and easily get a $\mathscr{I}$-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$,
where $\circ$ is the function concatenation. This $\iota\circ\mu$
may or may not be a QIVPM as shown in the following example. In the
four-dimensional Hilbert space with 
\begin{equation}
\iota'\left(x\right)=\begin{cases}
\imposs\,, & \textrm{ if }x=0\,;\\
\left[0,\tfrac{1}{2}\right]\,, & \textrm{ if }x\in\left(0,\tfrac{1}{4}\right]\,;\\
\unknown\,, & \textrm{ if }x\in\left(\tfrac{1}{4},\tfrac{3}{4}\right)\,;\\
\left[\tfrac{1}{2},1\right]\,, & \textrm{ if }x\in\left[\tfrac{3}{4},1\right)\,;\\
\necess\,, & \textrm{ if }x=1\,,
\end{cases}\label{eq:iota}
\end{equation}
the function~$\iota'\circ\mu_{\rho_{0}}^{\mathrm{\mathrm{B}}}$ induced
by $\rho_{0}=\frac{1}{4}\cdot\proj{0}+\frac{1}{4}\cdot\proj{1}+\frac{1}{4}\cdot\proj{2}+\frac{1}{4}\cdot\proj{3}$
is a QIVPM, but the function~$\iota'\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
induced by $\rho_{1}=\frac{1}{8}\cdot\proj{0}+\frac{1}{8}\cdot\proj{1}+\frac{1}{8}\cdot\proj{2}+\frac{5}{8}\cdot\proj{3}$
is \emph{not} a QIVPM. Although we could verify whether $\iota\circ\mu$
is a QIVPM or not directly, it is a long and tedious process. Therefore,
it is desirable to find some criteria when $\iota\circ\mu$ is a QIVPM.

>>>>

Recall in Sec.~\ref{sec:fuzzy}, we illustrate the non-constructive
postulates for the quantum probability measures first, and then introduce
the Born rule which induces a quantum probability measures from each
state. Since the postulates for QIVPMs in Sec.~\ref{sec:Interval-Uncertainty}
are also non-constructive, we also want to find a simple rule to construct
a QIVPM. When we generalize quantum probability measures to QIVPMs,
we replace the unit interval range~$\left[0,1\right]$ by a set of
intervals~$\mathscr{I}$. This replacement suggests a function~$\iota$
mapping a number~$x\in\left[0,1\right]$ to an interval~$\iota\left(x\right)\in\mathscr{I}$.
The function~$\iota$ can then be concatenated with a quantum probability
measure~$\mu:\events\rightarrow\left[0,1\right]$ and easily get
an interval-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$,
where $\circ$ is the function concatenation. However, the concatenated
function~$\iota\circ\mu$ may or may not be a QIVPM. For example,
in a four-dimensional Hilbert space, consider the function 
\begin{equation}
\iota'\left(x\right)=\begin{cases}
\imposs\,, & \textrm{ if }x=0\,;\\
\left[0,\tfrac{1}{2}\right]\,, & \textrm{ if }x\in\left(0,\tfrac{1}{4}\right]\,;\\
\unknown\,, & \textrm{ if }x\in\left(\tfrac{1}{4},\tfrac{3}{4}\right)\,;\\
\left[\tfrac{1}{2},1\right]\,, & \textrm{ if }x\in\left[\tfrac{3}{4},1\right)\,;\\
\necess\,, & \textrm{ if }x=1\,.
\end{cases}\label{eq:iota}
\end{equation}
While the function~$\iota'\circ\mu_{\rho_{0}}^{\mathrm{\mathrm{B}}}$
induced by $\rho_{0}=\frac{1}{4}\cdot\proj{0}+\frac{1}{4}\cdot\proj{1}+\frac{1}{4}\cdot\proj{2}+\frac{1}{4}\cdot\proj{3}$
is a QIVPM, the function~$\iota'\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
induced by $\rho_{1}=\frac{1}{8}\cdot\proj{0}+\frac{1}{8}\cdot\proj{1}+\frac{1}{8}\cdot\proj{2}+\frac{5}{8}\cdot\proj{3}$
is \emph{not} a QIVPM. Although we could verify whether $\iota\circ\mu$
is a QIVPM or not for any pair of $\iota$ and $\mu$ individually,
the verification process is long and tedious. Therefore, it is desirable
to have some easy criteria to get a QIVPM~$\iota\circ\mu$.
